\documentclass[margin,line,a4paper]{resume}

\begin{document}
\name{\Large Hattie Davis}
\begin{resume}

% Contact Information
\section{\mysidestyle Contact\\Information}

Woodgate House, Bath Road                     \hfill mobile: 0791 676 7677         \vspace{0mm}\\\vspace{0mm}
Marlborough SN8 1NN                           \hfill e-mail: hattie.davis@cssd.ac.uk  \vspace{0mm}\\\vspace{-4.5mm}

% Education
\section{\mysidestyle Education}

\textbf{Central School of Speech \& Drama}
\textsl{BA (Hons) Drama, Applied Theatre \& Education} \hfill \textbf{2007 -- 2010}\vspace{-3mm}\\\vspace{-1mm}
\begin{list2}
    \item Modules included: Experience in Context, Professional Placement
\end{list2}\vspace{-1.5mm}

\textbf{St. John's School, Marlborough}
\hfill \textbf{2003 -- 2007}\vspace{-3mm}\\\vspace{-1mm}%
\begin{list2}
    \item A Levels: Drama (Grade A) English Literature (Grade A), English Language (Grade B)
    \item GCSEs: Drama (Grade A), Media Studies (Grade A), English (Grade A), Science (Grade B), Maths (Grade B), Latin (Grade B), Art (Grade B), German (Grade B)
\end{list2}\vspace{-1.5mm}


% Professional Experience
\section{\mysidestyle Professional\\Experience}

\textbf{Central School of Speech and Drama}, London \vspace{2mm}\\\vspace{1mm}
\textsl{Usher} \hfill \textbf{June –- July 2009}\\
Worked sporadically for flexible hours, providing support to the team, creating a friendly and approachable atmosphere for customers whilst performing in a number of different tasks.

\textbf{Company of Angels}, London \vspace{2mm}\\\vspace{1mm}
\textsl{Professional Placement} \hfill \textbf{October –- December 2009}\\
As part of my course I went on a placement with a theatre company. I worked in the office, keeping reliable hours, and supporting the staff that worked there.

\textbf{Monsoon}, Malborough \vspace{2mm}\\\vspace{1mm}
\textsl{Sales Assistant} \hfill \textbf{July -- August 2008}\vspace{1.5mm}\\\vspace{0mm}
My summer job that year was at Monsoon, helping out during the very busy sale period. I had to learn the product line quickly so that I could make informed suggestions to ladies in the changing rooms, I was also in charge of keeping the aesthetic standards of the shop.

\textbf{Helen \& Douglas House}, Marlborough \vspace{2mm}\\\vspace{1mm}
\textsl{Sales Assistant} \hfill \textbf{July -- September 2007}\\
This was a voluntary job. I usually worked upstairs and helped customers, with the responsibility of taking payments. I also had a secondary role of sorting out things to go onto the shop floor.

\textbf{Caf\'{e} Uno}, Marlborough \vspace{2mm}\\\vspace{1mm}
\textsl{Waitress} \hfill \textbf{January -- September 2007}\\
I worked part-time as a waitress for Caf\'{e} Uno, having to always maintain and enthusiastic and hardworking approach whilst being suitably attired and flexible about working hours.

\textbf{Art Meets Matter}, Bath \vspace{2mm}\\\vspace{1mm}
\textsl{Temporary Assistant} \hfill \textbf{July -- September 2006}\\
My main duties included that of packing up products to go to customers, and responding to queries on the phone. I cultivated a professional attitude and telephone manner as a result.

\textbf{Urban Rustics}, Devizes \vspace{2mm}\\\vspace{1mm}
\textsl{Sales Assistant} \hfill \textbf{June 2004}\\
I went here for work experience and my main duties included helping customers, taking payments, and arranging window displays.

% Skills
\section{\mysidestyle Interests \& Skills} 
I am friendly, enthusiastic and quick to learn new skills. Eager to gain experience, especially within fashion as I hope one day to set up my own shop. I have great IT and technological abilities and am competent in the use of Windows, OS X, Microsoft Office and Web authoring. I am proficient at and have experience of point-of-sale and customer service. I bring my creative background and artistic flair to everything I do, making sure that I achieve it to a high standard.


% Referees
\section{\mysidestyle Referees} 
{\sl Available on request.}

\end{resume}
\end{document}


