%\documentclass[margin,line]{resume}
\documentclass{resume}

% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%\usepackage{helvetica}
%\usepackage{microtype}
%\usepackage{charter}

\usepackage{libertine}

%\usepackage{fontspec,xltxtra,xunicode}
%\defaultfontfeatures{Mapping=tex-text,Numbers=Lining}
%\setromanfont[Mapping=tex-text]{Hoefler Text}

\begin{document}
\name{Lee Phillip Gent, MSci}
\address{89 Barley Leaze\\Chippenham\\SN14 6GW\\UK}
\address{lee@leegent.net\\+44 7748 183797}

\begin{resume}

\section{Programming}
{\small
\begin{tabular}{rl}
\textbf{Languages} & C++, C, C\#, PHP, XML, Python, Obj-C, SQL, ECMAScript, Java, HTML \& CSS \\
\textbf{Toolkits \& APIs} & Qt 4, STL \& TR1, gSOAP, Boost, Win32, POSIX, .NET, VxWorks, SQLite \\
\textbf{Technologies} & OOP, SOAP \& Web Services, BSD Sockets \\
\textbf{Environments \& Tools} & Visual Studio 200x, Eclipse, GCC, XCode, Subversion, Git \\
\textbf{Operating Systems} & Windows (all versions \& Server 2003), Linux, OS X, Solaris 10
\end{tabular}
}
\section{Objective}
Engineering or IT Administration position where knowledge and use of object-oriented programming principles, modern tools, networking experience, excellent problem-solving skills and a passion for technology can be used to help create high-quality software products.

\section{Employment}

\employer{\textsl{Aria Networks, Ltd}}
\title{\bf{Lead Software Architect}}
\dates{2009 -- current}
\location{Chippenham, UK}
\begin{position}
Led a team in the design and development of the second major version of the flagship, portable network planning software with a full plugin/component-based architecture.  Built with C++ \& Qt 4.\vspace{1mm}\\
Supported teams performing sustained development of all company products at every level (requirements, architecture, design \& development).\vspace{1mm}\\
Supported company executive and sales teams in costing and effort estimations for new projects.\vspace{1mm}\\
Developed critical features in a large, bespoke development project using ECMAScript.  Wrote SOAP client in C with gSOAP.\vspace{1mm}\\
Ported performance-critical portions of ECMAScript code to C++.
\end{position}

\employer{\textsl{Aria Networks, Ltd}}
\title{\bf{Lead Software Engineer}}
\dates{2006 -- 2009}
\location{Chippenham, UK}
\begin{position}
Designed, developed, maintained, deployed and supported a platform-portable GMPLS network planning and routing product based on genetic algorithms with desktop GUI written using Qt 4.  Used XML for data persistence.\vspace{1mm}\\
Supported a small team with sustained development and forking of the product into customised bespoke products.\vspace{1mm}\\
Led a small team in the development of a bespoke, platform-portable network management and planning tool for a large network vendor.\vspace{1mm}\\
Worked in a team to develop a bespoke real-time VxWorks GMPLS network routing engine in the C language for inclusion in an high-grade optical switch.  Required understanding and interface with customer software API.
\end{position}

\employer{\textsl{Aria Networks, Applied InSilico \& DNNI Ltd}}
\title{\bf IT \& Network Administrator}
\dates{2003 -- current}
\location{Chippenham, UK}
\begin{position}
Built and maintained physical and logical business infrastructure.\vspace{1mm}\\
Responsible for wired \& wireless Ethernet LAN, Windows Server 2003 AD PDC \& Exchange Server 2003, MS IIS \& RAS/VPN access.\vspace{1mm}\\
Responsible for GNU/Linux servers running Apache \& Lighttpd, MoinMoin wiki, Trac and Subversion servers.\vspace{1mm}\\
Responsible for physical and logical workstation maintenance, network security, company software policy \& strategy, procurement.
\end{position}

\employer{\emph{Applied InSilico, Ltd}}
\title{\bf Lead Software Engineer}
\dates{2005 -- 2006}
\location{Chippenham, UK}
\begin{position}
Tailored flagship artificial intelligence product for Life Sciences market.\vspace{1mm}\\
Provided support for large customer deployment of the platform.\vspace{1mm}\\
Added SOAP interface to platform and developed GUI client using new interface.\vspace{1mm}\\
Designed next generation of product as fully extendible object-oriented/plugin-based system.\vspace{1mm}\\
Developed software download bootstrap/auto-update mechanism to aid deployment and maintenance of product.
\end{position}

\employer{\emph{DNNI, Ltd}}
\title{\bf Lead Software Engineer}
\dates{2003 -- 2005}
\location{Chippenham, UK}
\begin{position}
Designed, developed, deployed and supported a distributed, high-performance, platform-portable artificial intelligence problem solving platform.\vspace{1mm}\\
Platform included server-side (headless) component (C++), headless remote clients (C) and remote administration GUI (C\#).\vspace{1mm}\\
Utilised generic and bespoke, patented neural-network algorithms coupled with genetic algorithms.\vspace{1mm}\\
Created and utilised a custom, bespoke TCP-based protocol to link components of the platform.\vspace{1mm}\\
Developed a suite of support \& aftermarket tools to accompany the platform.
\end{position}

\employer{\emph{Keele University}}
\title{\bf Computer Science Lab Demonstrator}
\dates{2001 -- 2003}
\location{Staffordshire, UK}
\begin{position}
Administered, monitored, provided assistance to and taught first year computer science students during their laboratory practical (Java programming) sessions.\vspace{1mm}\\
Similarly for second year students; involved heavily with Java, OOP, PHP, XHTML, CSS \& JavaScript.\vspace{1mm}\\
One-on-one mentoring as well as group teaching.
\end{position}

\employer{\emph{Words WorldWide, Ltd.}}
\title{\bf Software Engineer}
\dates{2001 -- 2002}
\location{Ponteland, UK}
\begin{position}
Designed, developed and maintained a variety of small software solutions and projects for internal use, utilising MFC 7 as well as distributed project management.\vspace{1mm}\\
Maintained and sustained development of several business-critical applications, as well as designing and developing new tools to interface with third-party applications. Involved COM, Automation and NT Security.
\end{position}

\section{Education}

\employer{\emph{Keele University}}
\title{\bf Astrophysics \& Computer Science}
\dates{1999 -- 2003}
\location{MSci. (Hons) -- Second Class First Division}
\begin{position}
Project work included building a distributed agent system \& review of security systems.\vspace{1mm}\\
Founder, Treasurer \& Server Administrator of Student Computer Society.\vspace{1mm}\\
Awarded Science Demonstrator Award for lab teaching activities.\vspace{1mm}\\
Member of Staff-Student Liaison Committee, Halls of Residence Council.\vspace{1mm}\\
Recognised as Microsoft Most Valuable Student for UK pilot programme.
\end{position}

\section{Referees} 
\textsl{Available on request.}
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Jay Perrett}                 &  \textbf{Daniel King}                     \\
%Chief Technology Officer                &  Senior Consultant                        \\
%Aria Networks Ltd.                      &  Old Dog Consulting Ltd.                  \\
%Chippenham, UK                          &  Llangollen, UK                           \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}

\end{resume}
\end{document}

