\documentclass[a4paper]{letter}
\usepackage{geometry}
\usepackage{charter}
\usepackage{microtype}
\usepackage{hyperref}

\signature{Lee Gent}
\address{22 Morse Close \\ Chippenham \\ SN15 3FY UK}
\begin{document}

\begin{letter}{}
\opening{Dear Valve,}

I would like to considered for the positions of Senior Software Engineer or Software Engineer for Steam as advertised on the Valve website.

I am an avid gamer as well as a qualified and experienced C++ software engineer, having lived and breathed computer games and programming since the Sinclair Spectrum.  I am particularly interested in Valve because of the affinity I feel for Valve games (I am a massive Half-Life fan) and the pioneering work of Steam, which I respect and admire both as a software project and for its revolutionary effect on the market.

My love of games and gaming extends beyond their entertainment value; I am very much interested in the culture of gaming and the use of games as a storytelling medium every bit as important as cinema and literature.  I have founded and managed several long-running gaming societies, FPS clans and MMORPG guilds.  I am also very familiar with Steam and urge you to examine my Steam profile: \url{http://steamcommunity.com/id/mournkaye}.

The work I have done on remote, distributed and client-server solutions is especially relevant to Steam - indeed Steam was a source of inspiration for me when designing a digital delivery mechanism for our own product.  I have practical experience on a large number of user-facing element technologies and techniques as well as back-end and middleware elements and direct you to the attached resum\'{e} for more details.  I am also a proponent of open-source software and regularly use OSS libraries in my own projects.

I believe I can enrich Valve with my relevant engineering skills, good humour and interpersonal skills, thirst for experience and love of gaming.  I have no doubt that I could add value to a team responsible for building and growing a top-quality, market-leading software platform.

I would welcome the opportunity to be interviewed for one of these positions and can be reached at any time via e-mail (lee@leegent.net), telephone (+447748183797) or Skype (lee.gent).  If required I am also able to fly to Washington.  I am currently a United Kingdom resident but I am fully willing to relocate to Bellevue.

Many thanks for your time and consideration, I hope to hear from you soon.
\closing{Sincerely yours,}
\end{letter}
\end{document}

