% Cover letter using letter.sty
\documentclass[a4paper]{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Hattie Davis}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Someone\\Somewhere\\UK}

\begin{flushleft}
{\large\bf Hattie Davis}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill Woodgate House, Bath Road, Malborough SN8 1NN \\
\hfill 0791 676 7677
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear Ms. Oates,} 
 
\noindent Please find attached my Curriculum Vitae for a retail sales position in your Marlborough branch.
 
\noindent I'm particularly interested in this position, which relates strongly to my previous experience in sales and personal interest in ladies fashion.

\noindent I'm currently in my final year of University in London, and I believe I meet all the essential criteria of the position. My work over the course of my degree in Drama, Applied Theatre and Education has been rewarding and productive. However, I wish to expand my career further, into the world of retail and ladies fashion. I see this role as an integral part of my intended future career path, building on my previous achievements.
 
\noindent The position also has a definite correlation with my practical knowledge and experience. You'll see from my CV that I have been involved in jobs that require high levels of customer service, reliability and flexibility such as waitressing, ushering, teaching, and retail sales.

\noindent I feel that I am experienced and hard working enough to make an effective and useful contribution to Fenn Wright Manson, and I'm enthusiastic about the chance to join the team. I am available to work from 16th of March onwards.

\noindent Thank you for your consideration of my application. Please contact me should you require any further information.
 
\closing{Yours sincerely,} 
 

 
%\encl{}  				% Enclosures

\end{letter}
 

\end{document}






