\documentclass{letter}
\usepackage{geometry}
\usepackage{helvet}
\usepackage{times}
\usepackage{microtype}

\signature{Hattie Davis}
\address{Woodgate House \\ Marlborough \\ SN8 1NN}
\begin{document}
\sffamily
\begin{letter}{}
\opening{Dear Ms Newland,}

I am writing to apply for the Box Office Sales Clerk position advertised on your website.  As requested I am enclosing my current CV along with this letter of application.

The opportunities presented in this position are very important to me, being able to be part of the world of theatre is something that I am hugely passionate about - in whatever form that may be. I think my experience and education will make me a competitive candidate for this position and some of the key strengths that I possess include:
\begin{itemize}
\item A reliable, punctual, and hardworking demeanor.
\item Past ushering experience, and that of working in a more administrative role within a theatre company
\item A friendly, helpful and social approach to working.
\item Competent in the use of Windows, Mac OS and Linux computer systems
\end{itemize}

With a BA degree in Drama, Applied Theatre and Education, I have a full understanding of the requirements that such positions hold- and have a passion in the subject that I think would translate into my work and my interactions with customers. I also have past experience of learning and excelling at new skills as needed.

Please see my CV for additional information on my experience. References are available for any of the jobs listed on request.

I can be reached at any time via e-mail at \mbox{hattiesinbox@hotmail.com} or my phone, \mbox{07916 767 677}.

Thank you for your time and consideration. I look forward to speaking with you about this employment opportunity.

\closing{Sincerely,}
\end{letter}
\end{document}

